%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer | Server Load Balancing} % Job title
    {Google} % Organization
    {SunnyVale, CA, USA} % Location
    {Aug 2022 - Present} % Date(s)
    { \begin{cvitems} % Description(s) of tasks/responsibilities % GKE UBB Custom Metrics.
        % https://cloud.google.com/kubernetes-engine/docs/concepts/about-gke-inference-gateway
        \item {Designed and Implemented load balancing for ML/server workloads
          using GPU/TPU/KV-cache utilization. This achieved:}
        \itemindent=2em
          \item {96\% faster Time-to-First-Token P90 latency.}
          \item {60\% faster Normalized-Time-Per-Output-Token P90 latency.}
          \item {32\% faster overall throughput for prefix-heavy workloads.}
        \itemindent=0em
        % Bridge Server Client
        %\href{https://cloud.google.com/kubernetes-engine/docs/how-to/expose-custom-metrics}{system}
        \item {Led the design and implementation of a distributed load balancing
          client-server system with partner teams in Canada and Poland. This
          achieved:}
        \itemindent=2em
        \item {Multi-threaded, concurrent, sharded, distributed load
          balancing client-server resilient to regional outages.}
        \item {Cloud customers can balance service traffic along any
          utilization dimension.}
        \item {Vastly simpler configuration (50\% reduction in configuration programming effort.)
          for custom load balancing behavior.}
        \itemindent=0em
        \item {Automated end-to-end testing framework for 70\% reduction in overall manual effort.}
        \item {10x speedup for network design process with 15x reduction in
          memory resources for network topology graph data structures.}
        \item {Wrote graph traversal algorithms to efficiently traverse Google's
          network topology and detect single points of failure.}
        \item {Improved automation to re-map 25\% of all edge network customers
          to greatly improve customer cost center allocation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {NetApp} % Organization
    {SunnyVale, CA, USA} % Location
    {May 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {3x speedup for OS compile-update-reboot time for ONTAP virtual machines.}
        \item {Automated ONTAP cloud cluster setup configuration for dynamic load testing.}
        \item {2.7x speedup for WAFL scheduler client I/O latency with minimal
               slowdown (0.8x) to WAFL scheduler replication operations latency.}
        \item {Further optimized 3.5x speedup for client I/O and 1.2x speedup
               for replication operations with online random forest server
               load prediction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Software Engineer Intern} % Job title
    {ZODAJ} % Organization
    {Pittsburgh, PA, USA} % Location
    {May 2020 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Devised SMS and Android COVID-19 contact tracing for Senegal
               in partnership with Senegalese health authorities.}
        \item {Designed NoSQL, PostgreSQL databases along with AWS Lambda
               RESTful API for TCN protocol contact tracing.}
        \item {Directed and implemented all permissions and roles within ZODAJ
               for Amazon AWS databases.}
        \item {Created exposure overlap algorithm for \textit{n} people in a
               store that runs in max(O(\textit{k}) or O(\textit{n} log
               \textit{n})), where \textit{k} is overlap count.}
        \item {Wrote graph algorithms, discrete-time Markov chain SIR epidemic
               modeling for tracking infections.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Linux Systems Engineer Intern (DevOps)} % Job title
    {BOSCH ASEAN} % Organization
    {Singapore} % Location
    {May 21, 2019 - Aug 19, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Identified bottleneck in debugging failed builds and significantly
               reduced debug time via
           auto log extraction from QEMU disks on build servers}
        \item {Parallelized Jenkins pipeline to reduce deployment testing from 20 mins to 1 min}
        \item {Began migration of current inventory servers to new OCS inventory servers via Ansible for seamless configuration}
        \item {Authored Linux Debian package for unit tests automation (security/functionality) on new OS installations}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Data Analytics Intern} % Job title
%    {Eyeota Pte Ltd } % Organization
%    {Singapore} % Location
%    {Dec 13, 2017 – May 10, 2018} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Programmed data cleaning and classification of advertiser and buyer data from programmatic buy-side platforms}
%        \item {Extracted advertisers’ target demographic trends via both web-scraping and buyers’ purchasing data}
%        \item {Streamlined updates of daily, weekly, and monthly audience data sales revenue via complete process automation}
%      \end{cvitems}
%    }

%---------------------------------------------------------
%  \cventry
%    {Platoon Sergeant, Transport Formation} % Job title
%    {Singapore Armed Forces} % Organization
%    {Singapore} % Location
%    {Jan 4, 2016 – Nov 3, 2017} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Automated human resource and vehicle accounting of over 20 combat vehicle types and 400 individual units.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
%  \cventry
%    {Machine Learning Research Intern} % Job title
%    {A*STAR SIMTECH Research} % Organization
%    {Singapore} % Location
%    {Jun 1, 2014 – Dec 31, 2014} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Selected as 6 of 1,140 students in my high school, Hwa Chong Institution, for a machine learning research internship}
%        \item {Utilized k-means clustering, partial least squares regression, extreme learning machine, and multiple linear regression to predict ink cartridge lifespans with industry standard of > 97\% accuracy, thus eliminating destructive batch-testing}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
